Response to the defense feedback

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Overview}
Figure~\ref{chapter5:fig:workflow} shows an overview of our side-channel leakages quantification tool. Given the source code of a victim program, \ctool{} can find the address-based side-channel leakages by fuzzing the victim program. To assist the illustration, we divide the workflow of ~\ctool{} into three steps. For the first step, we build the target program from the source code. After that, we give them random inputs to the victim program and run the target program and record the each of the addresses in the binary file is hit or not, and store the information in a bitmap. Next, we analyze the side-channel leakage from the address access bitmap. We split the address space into several segments to speed up the comparison according to the meta information. Finally, \ctool{} generates the final leakage report. For each leakage site, \ctool{} gives a conservative estimation of the information leakage. Every leakage site in the report is a true leakage, and there are no false positives.

@@

\subsection{Step 1: Fuzzing}
After we build the software into the binary executable, we give the
binary executable random inputs. For cryptography libraries, the input
is the encryption key. For non-cryptography libraries, the input could
be images, text, and information in another format. Encryption
algorithms like AES and DES take an array representing the secrets. We
generate the random input by flipping each bit of the keys. Some other
programs also take a buffer as the input. The buffer may contain 
redundancy information and follow a specific format. So not every input
that satisfies the input length is a valid input. Under the
circumstance, we have a dictionary that contains the input. For
example, crypto libraries usually take PKCS \#1 as the input of the
RSA private key. We generate a list of valid
keys and use the keys to sample the program. Due to the enormous search
space, we cannot iterate every input. However, our method can give a
conservative estimate of each leakage site.

>>>>

\subsection{Overview}
Figure~\ref{chapter5:fig:workflow} shows an overview of our side-channel leakages quantification tool. Given the source code of a victim program, \ctool{} can find the address-based side-channel leakages by fuzzing the victim program. To assist the illustration, we divide the workflow of ~\ctool{} into three steps. For the first step, we build the target program from the source code. After that, we give them random inputs to the victim program and run the target program and record each of the addresses in the binary file is hit or not, and store the information in a bitmap. Next, we analyze the side-channel leakage from the address access bitmap. We split the address space into several segments to speed up the comparison according to the meta information. Finally, \ctool{} generates the final leakage report. For each leakage site, \ctool{} gives a conservative estimation of the information leakage. Every leakage site in the report is a true leakage, and there are no false positives.

@@

\subsection{Step 1: Fuzzing}
After we build the software into a binary executable, we give the
binary executable random inputs. For cryptography libraries, the input
is the encryption key. For non-cryptography libraries, the input could
be images, text, and information in another format. Encryption
algorithms like AES and DES take an array representing the secrets. We
generate the random input by flipping each bit of the keys. Some other
programs also take a buffer as the input. The buffer may contain 
redundancy information and follow a specific format. So not every input
that satisfies the input length is a valid input. Under the
circumstance, we have a dictionary that contains the input. For
example, crypto libraries usually take PKCS \#1 as the input of the
RSA private key. We generate a list of valid
keys and use the keys to sample the program. Due to the enormous search
space, we cannot iterate every input. However, our method can give a
conservative estimate of each leakage site.
